Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
filter change/load as per DM-12573

{\bf Filter Changes -- } The maximum time for filter change is $120$ seconds: $30$ seconds for the telescope to reorient the camera to its nominal zero angle position on the rotator, and $90$ seconds to the camera subsystem for executing the change (OSS-REQ-0293; \citeds{LSE-30}). Assuming that most Special Programs would be designed to keep overheads $<100\%$ and would be using standard $30$ second visits, the filter change time indicates that it is likely that at least $4$ exposures in a given filter would be obtained between filter changes -- but this is not actually a technical boundary.

{\bf Filter Carousel Loads -- } As described in \citeds{Document-28382}, the filter carousel can hold five of the six LSST filters at a time, and filter loads are done in the day. The system is designed to support $3000$ loads and $100000$ filter changes in $15$ years, which is an average of $17$ changes per night (after accounting for filter changes during calibrations). Individual filters will support $30000$ changes in $15$ years. Based on these technical boundaries, we know that there will never be data in more than five filters in a given night.

>>>>

{\bf Filter Changes -- } The maximum time for filter change is $120$ seconds: $30$ seconds for the telescope to reorient the camera to its nominal zero angle position on the rotator, and $90$ seconds to the camera subsystem for executing the change (OSS-REQ-0293; \citeds{LSE-30}).
Assuming that most Special Programs would be designed to keep overheads $<100\%$ and would be using standard $30$ second visits, the filter change time indicates that it is likely that at least $4$ exposures in a given filter would be obtained between filter changes, but this is not actually a technical boundary. 
The filter change mechanism is designed to undergo a total of $100000$ changes over its lifetime, and each filter is designed to support up to $30000$ changes over its lifetime, where lifetime is $15$ years (an average of $17$ changes per night after accounting for filter changes during calibrations).
During a given observing night, the system could support as many changes involving the 5 filters loaded in the carousel as desired (see filter change memorandum \url{ls.st/spt-494}).

{\bf Filter Carousel Loads -- } The filter carousel can hold five of the six LSST filters at a time.
The system is designed to support $3000$ loads in $15$ years (\url{ls.st/spt-494}).
Filter loads are only done in the day, and there will never be data in more than five filters in a given night.
